Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-12 paper.qmd
Updated Figure 13

trimesh_removed_gau_tsne + trimesh_removed_gau_umap + trimesh_removed_gau_pacmap +
five_gau_proj_tsne_model1 + five_gau_proj_umap_model1 + five_gau_proj_pacmap_model1 + 
  five_gau_proj_tsne_model2 +
  five_gau_proj_umap_model2 + five_gau_proj_pacmap_model2 +
  plot_layout(guides = "collect", nrow = 3) &
  theme(legend.position='none')
```

@@

error_plot_mnist <- plot_mse(error_mnist) +
  scale_x_continuous(breaks = sort(
    unique(error_mnist$a1))[append(seq(1, length(unique(error_mnist$a1)), 
                                       by = 5), 24)]) +
  scale_color_manual(
    values=c('#e41a1c','#377eb8',"#ff7f00", 
             '#984ea3', '#999999', '#a65628')) +
  theme(aspect.ratio=1.5)

>>>>

trimesh_removed_gau_tsne + trimesh_removed_gau_umap + trimesh_removed_gau_pacmap +
five_gau_proj_tsne_model1 + five_gau_proj_umap_model1 + five_gau_proj_pacmap_model1 + 
  #five_gau_proj_tsne_model2 +
  #five_gau_proj_umap_model2 + five_gau_proj_pacmap_model2 +
  plot_layout(guides = "collect", nrow = 2) &
  theme(legend.position='none')
```

@@

error_plot_mnist <- plot_mse(error_mnist) +
  scale_x_continuous(breaks = sort(
    unique(error_mnist$a1))[append(seq(1, length(unique(error_mnist$a1)), 
                                       by = 5), 24)]) +
  scale_color_manual(
    values=c('#a65628', '#984ea3', '#999999', 
             '#377eb8', '#ff7f00', '#e41a1c')) +
  theme(aspect.ratio=1.5)
